Telemetry Module for Solar Vehicle

### 2021-06-16 documentation/FinalPaper/paper.tex

\usepackage{cite}
\usepackage[pdftex]{graphicx}
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{comment}
\usepackage{textcomp}
\usepackage{xcolor}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}

\usepackage{url}

@@

\section{Design}
- Block Diagram and description of overall data flow

\section{Components}
\subsection{CAN bus}
% MCP
\subsection{RF network} % Steffan
The nRF24L01+ LoRa RF module is used to provide two-way communication between the solar car and support vehicle. The module includes a detachable antenna, power amplifier and low-noise amplifier to provide a theoretical range in excess of 1000 m at data rates of up to 2 Mbit/s. In addition to this, comprehensive driver libraries are provided by the manufacturer, making it very easy to integrate with our project.
The nRF24L01+ module uses the Enhanced Shockburst $\copyright$ packet structure to transmit messages over the 2.4 GHz ISM band. Messages contain a data payload of up to 32 bytes, allowing us comfortably to transmit one CAN telemetry message per packet \cite{shockburst}. Further, the package structure includes a preamble, address, packet and CRC bytes segments as shown in Figure \ref{fig:shockburst}. 
\begin{comment}
\begin{figure}[h]
    \centering
    \includegraphics[width=0.5\textwidth]{documentation/images/EnhancedShockburst.png}
    \caption{The Enhanced Shockburst $\copyright$ packet structure.}
    \label{fig:shockburst}
\end{figure}
\end{comment}

@@

\section{Discussion}
% variable length messages would reduce overhead -> but most messages cotain CAN and are optimized
%

@@

\bibliographystyle{IEEEtran}
\bibliography{IEEEabrv,../bib/paper}

\section{References}
\begingroup
\renewcommand{\section}[2]{}%
%\renewcommand{\chapter}[2]{}% for other classes
\begin{thebibliography}{}
\bibitem{wsc}
Bridgestone World Solar Challenge, 
URL: https://worldsolarchallenge.org/
\bibitem{ROAST}
Reports and source files provided by DTU ROAST
\bibitem{teensy}
Teensy microcontroller,
URL: https://www.pjrc.com/teensy/
\bibitem{C++}
Website for learning C++
https://www.learn-cpp.org/
\bibitem{ACAN}
Documentation,
https://github.com/pierremolinaro/acan
\bibitem{shockburst}
nRF24 transmission protocol, URL: https://lastminuteengineers.com/nrf24l01-arduino-wireless-communication/
\end{thebibliography}
\endgroup

>>>>

\usepackage[pdftex]{graphicx}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{float}
\usepackage{comment}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage[style=ieee]{biblatex}
\addbibresource{paper.bib}
\usepackage{url}

@@

\section{Design}
The overall system consists of three separate modules; the Solar Car Unit which communicates with the Support Vehicle Unit via a wireless RF connection, which in turn interacts with the Support Vehicle Laptop through a serial USB connection. The schematic for the system is outlined in Figure \ref{fig:schematic}. 
\begin{figure}[H]
    \centering
    \includegraphics[width=0.5\textwidth]{documentation/images/schematic.png}
    \caption{Overview of the system's components in block diagram form.}
    \label{fig:schematic}
\end{figure}

\section{Components}
\subsection{CAN bus}
% MCP
\subsection{RF network} % Steffan
The system uses two nRF24L01+ transceivers to provide a bidirectional connection between the Solar Car and Support Vehicle over the 2.4 GHz ISM band. The module features a detachable antenna, power amplifier and low-noise amplifier to provide a theoretical range in excess of 1000 m at data rates of up to 2 Mbit/s.

An advantage of using an off-the-shelf RF module is the automated message protocol, known as Enhanced Shockburst$^{\copyright}$.

The nRF24L01+ module uses the Enhanced Shockburst $\copyright$ packet structure to transmit messages over the 2.4 GHz ISM band. Messages contain a data payload of up to 32 bytes, allowing us comfortably to transmit one CAN telemetry message per packet \cite{shockburst}. Further, the package structure includes a preamble, address, packet and CRC bytes segments as shown in Figure \ref{fig:shockburst}.

\begin{figure}[h]
    \centering
    \includegraphics[width=0.5\textwidth]{documentation/images/EnhancedShockburst.png}
    \caption{The Enhanced Shockburst $\copyright$ packet structure.}
    \label{fig:shockburst}
\end{figure}

@@

\section{Discussion}
% variable length messages would reduce overhead -> but most messages contain CAN and are optimized
%

@@

\printbibliography
